Increasing the mortality gap? Social inequality in mortality among elderly and adults in Northern Sweden 1851--2013\footnote{Session "Health, morbidity, and mortality" at the Nordic Demographic Symposium 14--16 June 2017, Turku, Finland}

### 2017-10-09 cape.Rnw
Changing title

\title{Increasing the mortality gap? Social inequality in mortality among 
elderly and adults in Northern  Sweden 1851--2013\footnote{Session "Health, 
morbidity, and mortality" at the Nordic Demographic Symposium 14--16 June 2017, 
Turku, Finland}
}

>>>>

\title{Life course and long-term perspectives of social inequality in mortality among 
elderly and adults in Northern  Sweden 1801--2013\footnote{Session "Social inequalities in health at older ages: life course perspectives" at the XXVIII International Population Conference 29 October--4 November 2017, Cape Town, South Africa}
}
